### 2025-02-27 scripts/Paper-analysis.Rmd
one rep per gene family analysis

>>>>

### All hard shell vs. accessory, one representative per gene family

We subsampled to one representative per gene family and the same number of hard shell and accessory genes, whichever was smaller (PTU-Bac37 was the only one that had more hard shell than accessory genes). 
```{r}
core_k6 = read.csv('~/Downloads/trieste/one_per_family/all_core_k6.csv')
accessory_k6 = read.csv('~/Downloads/trieste/one_per_family/all_accessory_k6.csv')
merge_k6 = merge(core_k6, accessory_k6, by="word")
merge_k6$diff = merge_k6$score.y-merge_k6$score.y
merge_k6$palindrome = ifelse(merge_k6$word %in% palindromes,
                             "palindrome", "other")
ggplot(merge_k6, aes(score.x-score.y))+
  geom_histogram()+
  facet_wrap(~palindrome)
```
